---
title: "CLT"
author: "kimberly lemus munoz"
date: '2022-06-08'
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
origmean<-mean(my1000)
origianlSD<-sd(my1000)
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

NO, it's not unimodal it have two peaks.The peaks are about the same size.The original data is `r origmean` standard devation is `r origianlSD`.




Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
sample2mean<-mean(x.avg)
sample2SD<-sd(x.avg)
```


The plot is not unimodal the plot have  3 peaks of it and they are not the same side.The peaks of the end are the same side while the middle is the above them.The average mean is `r sample2mean` standard deviation `r sample2SD `.



```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
sample4mean<-mean(x.avg)
sample4SD<-sd(x.avg)
```



The mean for the sample 4 is `r sample4mean`  with sample 4 standard devation is `r sample4SD`.


