---
title: "CLT"
author: "kimberly lemus munoz"
date: '2022-06-08'
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
origmean<-mean(my1000)
origianlSD<-sd(my1000)
options(digits = 1)
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

NO, it's not unimodal it have two peaks.The peaks are about the same size.The original data is `r origmean` standard deviation is `r origianlSD`.




Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
sample2mean<-mean(x.avg)
sample2SD<-sd(x.avg)
```


The plot is not unimodal the plot have  3 peaks of it and they are not the same side.The peaks of the end are the same side while the middle is the above them.The average mean is `r sample2mean` standard deviation `r sample2SD `.



```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
sample4mean<-mean(x.avg)
sample4SD<-sd(x.avg)
```

The mean for the sample 4 is `r sample4mean`  with sample 4 standard devation is `r sample4SD`.There's 5 peaks in this sample 4 ,there is 4 people are not liking Kim which is 1 out 4.There is 2 out of 4 liking her in another peak there's 3 out 4 people liking her and the other peak was 4 out 4 liking her.

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
sample9mean<-mean(x.avg)
sample9SD<-sd(x.avg)
```
The mean for the sample 9 is `r sample9mean`  with sample 9 standard deviation is `r sample9SD`.There are 4 peaks on sample 9 which also tell us this plot isn't unimodal. Two of the peaks are at the same level which at slightly above 0.15. The other 2 are above 0.025.this peaks shown of the 4 out 4 people like her while some don't. Every time we do a higher sample the standard deviation keeps going down drastically. While with the mean it goes down slowly.When comparing to the original data.



```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
sample16mean<-mean(x.avg)
sample16SD<-sd(x.avg)
```

The mean for the sample 16 is `r sample16mean`  with sample 16 standard deviation is `r sample16SD`.This has only one peak, this sample 16  is Unimodal. It seems that this peak is above 0.03.  Every time we do a higher sample the standard deviation keeps going down drastically. While with the mean it goes down slowly.When comparing to the original data.



```{r}
numb = 25
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 25")
sample25mean<-mean(x.avg)
sample25SD<-sd(x.avg)
```



The mean for the sample 25 is `r sample25mean`  with sample 25 standard deviation is `r sample25SD`.
This has 1 peaks in sample 25 which tell us that it’s  unimodal. One peak is at the exact point of 0.05.




```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
sample36mean<-mean(x.avg)
sample36SD<-sd(x.avg)
```

The mean for the sample 36 is `r sample36mean`  with sample 36 standard deviation is `r sample36SD`.In this one, there is only one peak in this sample 36 this sample is unimodal. The one peak is at 0.05. Every time the standard deviation it goes down drastically while with the mean it seems to go down slowly.When comparing to the original data.





